
\documentclass[a4paper, 12pt, color, final]{moderncv}

\moderncvstyle{classic}
\definecolor{color0}{rgb}{0,0,0}
\definecolor{color1}{rgb}{0.50,0.44,0.60}
\definecolor{color2}{rgb}{0.55,0.55,0.55}

\nopagenumbers{}

\usepackage[utf8]{inputenc}

\usepackage[scale=0.80]{geometry}
\setlength{\hintscolumnwidth}{3cm}

% personal data
\name{Andrei}{Tsialiatka}
\title{Software engineer}
\address{Minsk}{Belarus}
\email{steepashka1love@gmail.com}
\social[linkedin]{atelyatko}
\social[github]{letmecnsooit}

\begin{document}
\makecvtitle

\section{Employment History}
\cventry{September 2017 -- Present}{Software Developer}{Itransition Group}{Minsk}{}{}

\section{Projects}

% \cventry{2021--present}{HF}{}{}{}{
% \begin{itemize}%
% \item //Description
% \item \textbf{Tools}: //Tools
% \end{itemize}}

\cventry{2020--2021}{Chromatography results processing}{}{}{}{
\begin{itemize}%
    \item A next-gen version of the original application which allows users to process and
    control different steps and stages of chromatography results. The application
    provides an ability to create plots for chromatography result peaks, apply integration
    filters for peaks, do system suitability checks to verify the results of integration and
    calibration steps, create user-specific workflows, apply permissions for users to give
    an access to work on a specific area of processing.
    \item \textbf{Tools}: ASP.NET Core 3.1, AWS (DocumentDB, S3), Docker, Angular 11, Typescript,
    D3.js, Angular Material, Wijmo, Karma, Jasmine, SpecFlow.
\end{itemize}}

\cventry{2017--2020}{Healthcare assistant}{}{}{}{
\begin{itemize}
    \item A complex healthcare solution that is aimed at helping people with chronic
    pain. Development includes several mobile applications, as well as separate web
    application along with a range of custom RESTful APIs. Main features of the project:
    \begin{itemize}
        \item RTC communication (audio/video calling, text chatting across multiple platforms);
        \item Activity tracker integration (Fitbit, Apple Health);
        \item Assessment module that defines a custom course of actions for the patient;
        \item Elaborate reporting/statistics modules for patients and counselors;
        \item HIPAA compliance;
    \end{itemize}
    \item \textbf{Tools}: ASP.NET Web API 2, Angular 6, Bootstrap 3, Dapper ORM, TokBox, Kendo
    UI, Telerik Reporting Tools, OData v4, C\# 7, TypeScript, Karma, Jasmine, Git.
\end{itemize}}

\cventry{2017--2020}{Utilization review processing}{}{}{}{
\begin{itemize}
    \item A service that provides prospective, concurrent and retrospective review of the
    medical necessity of services. The project facilitates the timely and appropriate
    treatment of injured employees while providing employers with greater financial
    controls; Provides an ability to estimate the cost of physicians and nurses working
    processes based on different UR cases criterias; Allows to generate a huge amount
    of reports with different metrics and criterias. Provides an ability to determine state
    workers compensation plans by using industry standard guidelines such as ACOEM
    \& ODG. Permission-based engine to restrict users to have an access to different
    application’s areas.
    \item \textbf{Tools}: JetBrains Rider IDE, Git, Bitbucket, IIS 7, MS SQL Server, SQL Server Profiler,
    SQL Server Management Studio, Postman, ASP.NET Web API 2, Entity Framework
    6, OData v4, DocX, EPPlus, Telerik Reporting Tools, Autofac, NUnit, AngularJS 1.6,
    KendoUI, Twitter Bootstrap 3, LESS, Webpack, npm, KendoUI, Babel, HTML5, CSS3,
    Jasmine.
\end{itemize}}

\section{Education}
\cvitem{2015--2019}{
    \textbf{Belarussian State University of Informatics and Radioelectronics}; \newline
    Faculty of Computer Systems and Networks; \newline
    Software for Information Technologies; \newline
    Bachelor's degree.
}
\cvitem{2019--2020}{
    \textbf{Belarussian State University of Informatics and Radioelectronics}; \newline
    Faculty of Computer-Aided Design; \newline
    Labor Protection and Ergonomics; \newline
    Master's degree.
}

\section{Skills}
\subsection{Main:}
\cvitem{}{ASP.NET Core, Angular, Azure, SQL, Git, NoSQL, Docker, AWS, React, TypeScript. }
\subsection{Experience with:}
\cvitem{}{TeamCity, Azure DevOps, Go, Python, \LaTeX. }

\section{Languages}
\cvitemwithcomment{English}{Advanced}{}
\cvitemwithcomment{Belarusian}{Native speaker}{}
\cvitemwithcomment{Russian}{Native speaker}{}

\end{document}
